Bayesian Hierarchical Modeling: An Introduction and Reassessment

### 2022-08-17 C - Tutorial Normal Model Rstan/Online Supplement C - Bayesian Hierarchical Modeling in rstan.Rmd
Updates package versions

- For the document layout: *rmarkdown* [Version 1.16; @R-rmarkdown], *papaja* [Version 0.1.0.9842; @R-papaja], *knitr* [Version 1.25; @R-knitr], *kableExtra* [Version 1.1.0; @R-kableExtra]
- For data structuring: *LaplacesDemon* [Version 16.1.4; @R-LaplacesDemon], *plyr* [Version 1.8.4; @R-plyr], *dplyr* [Version 0.8.3; @R-dplyr], *readr* [Version 1.3.1; @R-readr]
- To fit the model: *rstan* [Version 2.19.2; @R-rstan]
- For the visualization of the results: *lattice* [Version 0.20.38; @R-lattice], *ggplot2* [Version 3.3.2; @R-ggplot2], *Rmisc* [Version 1.5; @R-Rmisc], *devtools* [Version 2.2.1; @R-devtools], *gghalves* [Version 0.1.0; @R-gghalves], *bayesplot* [Version 1.7.1; @R-bayesplot], *brms* [Version 2.13.0; @R-brms_a; @R-brms_b], *gridExtra* [Version 2.3; @R-gridExtra], *tibble* [Version 3.0.2; @R-tibble]
- For model comparison: *bridgesamping* [Version 1.0.0; @R-bridgesampling]

>>>>

- For the document layout: *rmarkdown* [Version 2.9; @R-rmarkdown], *papaja* [Version 0.1.0.9997; @R-papaja], *knitr* [Version 1.33; @R-knitr], *kableExtra* [Version 1.3.4; @R-kableExtra]
- For data structuring: *LaplacesDemon* [Version 16.1.6; @R-LaplacesDemon], *plyr* [Version 1.8.6; @R-plyr], *dplyr* [Version 1.0.7; @R-dplyr], *readr* [Version 2.0.0; @R-readr], *truncnorm* [Version 1.0.8; @R-truncnorm]
- To fit the model: *rstan* [Version 2.21.3; @R-rstan]
- For the visualization of the results: *lattice* [Version 0.20.44; @R-lattice], *ggplot2* [Version 3.3.2; @R-ggplot2], *Rmisc* [Version 1.5; @R-Rmisc], *devtools* [Version 2.4.2; @R-devtools], *gghalves* [Version 0.1.1.9000; @R-gghalves], *bayesplot* [Version 1.8.1; @R-bayesplot], *brms* [Version 2.16.3; @R-brms_a; @R-brms_b], *gridExtra* [Version 2.3; @R-gridExtra], *ggridges* [Version 0.5.3; @R-ggridges], *ggbeeswarm* [Version 0.6.0; @R-ggbeeswarm], *tibble* [Version 3.1.6; @R-tibble]
- For model comparison: *bridgesamping* [Version 1.1.2; @R-bridgesampling]

### 2022-08-17 D - Tutorial Normal Model brms/Online Supplement D - Bayesian Hierarchical Modeling in brms.Rmd
Updates package versions

- For the document layout: *rmarkdown* [Version 1.16; @R-rmarkdown], *papaja* [Version 0.1.0.9842; @R-papaja], *knitr* [Version 1.25; @R-knitr], *kableExtra* [Version 1.1.0; @R-kableExtra]
- For data structuring: *LaplacesDemon* [Version 16.1.4; @R-LaplacesDemon], *plyr* [Version 1.8.4; @R-plyr], *dplyr* [Version 0.8.3; @R-dplyr], *readr* [Version 1.3.1; @R-readr], *truncnorm* [Version 1.0.8; @R-truncnorm]
- To fit the model and for model comparison: *brms* [Version 2.13.0; @R-brms_a; @R-brms_b]
- For the visualization of the results: *lattice* [Version 0.20.38; @R-lattice], *ggplot2* [Version 3.3.2; @R-ggplot2], *Rmisc* [Version 1.5; @R-Rmisc], *devtools* [Version 2.2.1; @R-devtools], *gghalves* [Version 0.1.0; @R-gghalves], *bayesplot* [Version 1.7.1; @R-bayesplot], *gridExtra* [Version 2.3; @R-gridExtra], *ggridges* [Version 0.5.3; @R-ggridges], *ggbeeswarm* [Version 0.6.0; @R-ggbeeswarm], *tibble* [Version 3.0.2; @R-tibble]

>>>>

- For the document layout: *rmarkdown* [Version 2.9; @R-rmarkdown], *papaja* [Version 0.1.0.9997; @R-papaja], *knitr* [Version 1.33; @R-knitr], *kableExtra* [Version 1.3.4; @R-kableExtra]
- For data structuring: *LaplacesDemon* [Version 16.1.6; @R-LaplacesDemon], *plyr* [Version 1.8.6; @R-plyr], *dplyr* [Version 1.0.7; @R-dplyr], *readr* [Version 2.0.0; @R-readr], *truncnorm* [Version 1.0.8; @R-truncnorm]
- To fit the model and for model comparison: *brms* [Version 2.16.3; @R-brms_a; @R-brms_b]
- For the visualization of the results: *lattice* [Version 0.20.44; @R-lattice], *ggplot2* [Version 3.3.5; @R-ggplot2], *Rmisc* [Version 1.5; @R-Rmisc], *devtools* [Version 2.4.2; @R-devtools], *gghalves* [Version 0.1.1.9000; @R-gghalves], *bayesplot* [Version 1.8.1; @R-bayesplot], *gridExtra* [Version 2.3; @R-gridExtra], *ggridges* [Version 0.5.3; @R-ggridges], *ggbeeswarm* [Version 0.6.0; @R-ggbeeswarm], *tibble* [Version 3.1.6; @R-tibble]

### 2022-08-17 E - Tutorial Log-Normal Model Rstan/Online Supplement E - Bayesian Hierarchical Modeling in rstan - Log Model.Rmd
Updates package versions

- For the document layout: *rmarkdown* [Version 1.16; @R-rmarkdown], *papaja* [Version 0.1.0.9842; @R-papaja], *knitr* [Version 1.25; @R-knitr], *kableExtra* [Version 1.1.0; @R-kableExtra]
- For data structuring: *LaplacesDemon* [Version 16.1.4; @R-LaplacesDemon], *plyr* [Version 1.8.4; @R-plyr], *dplyr* [Version 0.8.3; @R-dplyr], *readr* [Version 1.3.1; @R-readr], *truncnorm* [Version 1.0.8; @R-truncnorm]
- To fit the model: *rstan* [Version 2.19.2; @R-rstan]
- For the visualization of the results: *lattice* [Version 0.20.38; @R-lattice], *ggplot2* [Version 3.3.2; @R-ggplot2], *Rmisc* [Version 1.5; @R-Rmisc], *devtools* [Version 2.2.1; @R-devtools], *gghalves* [Version 0.1.0; @R-gghalves], *bayesplot* [Version 1.7.1; @R-bayesplot], *brms* [Version 2.13.0; @R-brms_a; @R-brms_b], *gridExtra* [Version 2.3; @R-gridExtra], *ggbeeswarm* [Version 0.6.0; @R-ggbeeswarm], *tibble* [Version 3.0.2; @R-tibble]
- For model comparison: *bridgesamping* [Version 1.0.0; @R-bridgesampling]

>>>>

- For the document layout: *rmarkdown* [Version 2.9; @R-rmarkdown], *papaja* [Version 0.1.0.9997; @R-papaja], *knitr* [Version 1.33; @R-knitr], *kableExtra* [Version 1.3.4; @R-kableExtra]
- For data structuring: *LaplacesDemon* [Version 16.1.6; @R-LaplacesDemon], *plyr* [Version 1.8.6; @R-plyr], *dplyr* [Version 1.0.7; @R-dplyr], *readr* [Version 2.0.0; @R-readr], *truncnorm* [Version 1.0.8; @R-truncnorm]
- To fit the model: *rstan* [Version 2.21.3; @R-rstan]
- For the visualization of the results: *lattice* [Version 0.20.44; @R-lattice], *ggplot2* [Version 3.3.5; @R-ggplot2], *Rmisc* [Version 1.5; @R-Rmisc], *devtools* [Version 2.4.2; @R-devtools], *gghalves* [Version 0.1.1.9000; @R-gghalves], *bayesplot* [Version 1.8.1; @R-bayesplot], *brms* [Version 2.16.3; @R-brms_a; @R-brms_b], *gridExtra* [Version 2.3; @R-gridExtra], *ggbeeswarm* [Version 0.6.0; @R-ggbeeswarm], *tibble* [Version 3.1.6; @R-tibble]
- For model comparison: *bridgesamping* [Version 1.1.2; @R-bridgesampling]

### 2022-08-17 manuscript.Rmd
Update manuscript.Rmd
Updates package versions

A.S. is supported by the Research Talent Programme from the Dutch Research Council and the Dutch Ministry of Education, Culture and Science (NWO; grant number 406.18.556).

@@

The R code used for the analyses and figures in this manuscript, and `R` tutorials on BHMs are available on [our GitHub repository]().

@@

- Document layout: *rmarkdown* [Version 1.16; @R-rmarkdown], *papaja* [Version 0.1.0.9842; @R-papaja], *knitr* [Version 1.25; @R-knitr], *kableExtra* [Version 1.1.0; @R-kableExtra]
- Data analysis and cleaning: *LaplacesDemon* [Version 16.1.4; @R-LaplacesDemon], *plyr* [Version 1.8.4; @R-dplyr; @R-plyr], *dplyr* [Version 0.8.3; @R-dplyr], *readr* [Version 1.3.1; @R-readr], *crch* [Version 1.0.4; @R-crch_a; @R-crch_b; @R-crch_c; @R-crch_d], *foreign* [Version 0.8.71; @R-foreign], *Matrix* [Version 1.2.17; @R-Matrix], *tidyr* [Version 1.0.0; @R-tidyr], *truncnorm* [Version 1.0.8; @R-truncnorm] 
- Model fit and comparison: *rstan* [Version 2.19.2; @R-rstan], *brms* [Version 2.13.0; @R-brms_a; @R-brms_b], *BayesFactor* [Version 0.9.12.4.2; @R-BayesFactor], *bridgesampling* [Version 1.0.0; @R-bridgesampling]
- Visualization: *coda* [Version 0.19.3; @R-coda], *lattice* [Version 0.20.38; @R-lattice], *ggplot2* [Version 3.3.2; @R-ggplot2], *Rmisc* [Version 1.5; @R-Rmisc], *devtools* [Version 2.2.1; @R-devtools], *gghalves* [Version 0.1.0; @R-gghalves], *bayesplot* [Version 1.7.1; @R-bayesplot], *gridExtra* [Version 2.3; @R-gridExtra], *tibble* [Version 3.0.2; @R-tibble], *ggmcmc* [Version 1.4.1; @R-ggmcmc], *cowplot* [Version 1.0.0; @R-cowplot], *ggridges* [Version 0.5.1; @R-ggridges], *circlize* [Version 0.4.9; @R-circlize], *StanHeaders* [Version 2.19.0; @R-StanHeaders], *unikn* [Version 0.2.0; @R-unikn], *ggbeeswarm* [Version 0.6.0; @R-ggbeeswarm]
- Other: *Rcpp* [Version 1.0.3; @R-Rcpp_a; @R-Rcpp_b], *usethis* [Version 1.5.1; @R-usethis]

>>>>

This work was supported in part by an NWO Research Talent grant to A.M.S. (406.18.556) and a Veni grant from the NWO (VI.Veni.201G.019) to J.M.H.

@@

The R code used for the analyses and figures in this manuscript, and `R` tutorials on BHMs are available under an CC-BY-4.0 license on [our GitHub repository]().

@@

- Document layout: *rmarkdown* [Version 2.9; @R-rmarkdown], *papaja* [Version 0.1.0.9997; @R-papaja], *knitr* [Version 1.33; @R-knitr], *kableExtra* [Version 1.3.4; @R-kableExtra]
- Data analysis and cleaning: *LaplacesDemon* [Version 16.1.6; @R-LaplacesDemon], *plyr* [Version 1.8.6; @R-dplyr; @R-plyr], *dplyr* [Version 1.0.7; @R-dplyr], *readr* [Version 2.0.0; @R-readr], *crch* [Version 1.0.4; @R-crch_a; @R-crch_b; @R-crch_c; @R-crch_d], *foreign* [Version 0.8.81; @R-foreign], *Matrix* [Version 1.3.3; @R-Matrix], *tidyr* [Version 1.1.3; @R-tidyr], *truncnorm* [Version 1.0.8; @R-truncnorm] 
- Model fit and comparison: *rstan* [Version 2.21.3; @R-rstan], *brms* [Version 2.16.3; @R-brms_a; @R-brms_b], *BayesFactor* [Version 0.9.12.4.2; @R-BayesFactor], *bridgesampling* [Version 1.1.2; @R-bridgesampling]
- Visualization: *coda* [Version 0.19.4; @R-coda], *lattice* [Version 0.20.44; @R-lattice], *ggplot2* [Version 3.3.5; @R-ggplot2], *Rmisc* [Version 1.5; @R-Rmisc], *devtools* [Version 2.4.2; @R-devtools], *gghalves* [Version 0.1.1.9000; @R-gghalves], *bayesplot* [Version 1.8.1; @R-bayesplot], *gridExtra* [Version 2.3; @R-gridExtra], *tibble* [Version 3.1.6; @R-tibble], *ggmcmc* [Version 1.5.1.1; @R-ggmcmc], *cowplot* [Version 1.1.1; @R-cowplot], *ggridges* [Version 0.5.3; @R-ggridges], *circlize* [Version 0.4.13; @R-circlize], *StanHeaders* [Version 2.21.0.7; @R-StanHeaders], *unikn* [Version 0.4.0; @R-unikn], *ggbeeswarm* [Version 0.6.0; @R-ggbeeswarm]
- Other: *Rcpp* [Version 1.0.7; @R-Rcpp_a; @R-Rcpp_b], *usethis* [Version 2.0.1; @R-usethis]

### 2022-08-17 manuscript.tex
Updates package versions

\hypertarget{acknowledgement}{%
\section{Acknowledgement}\label{acknowledgement}}

@@

\begin{itemize}
\tightlist
\item
  Document layout: \emph{rmarkdown} {[}Version 1.16; Xie, Allaire, and Grolemund (2018){]}, \emph{papaja} {[}Version 0.1.0.9842; Aust and Barth (2018){]}, \emph{knitr} {[}Version 1.25; Xie (2015){]}, \emph{kableExtra} {[}Version 1.1.0; Zhu (2019){]}
\item
  Data analysis and cleaning: \emph{LaplacesDemon} {[}Version 16.1.4; Statisticat and LLC. (2020){]}, \emph{plyr} {[}Version 1.8.4; Wickham, François, Henry, and Müller (2019); Wickham (2011){]}, \emph{dplyr} {[}Version 0.8.3; Wickham, François, Henry, and Müller (2019){]}, \emph{readr} {[}Version 1.3.1; Wickham, Hester, and Francois (2018){]}, \emph{crch} {[}Version 1.0.4; Messner, Mayr, and Zeileis (2016); Messner, Mayr, and Zeileis (2017); Messner, Zeileis, Broecker, and Mayr (2014); Messner, Mayr, Zeileis, and Wilks (2014){]}, \emph{foreign} {[}Version 0.8.71; R Core Team (2018){]}, \emph{Matrix} {[}Version 1.2.17; Bates and Maechler (2019){]}, \emph{tidyr} {[}Version 1.0.0; Wickham and Henry (2019){]}, \emph{truncnorm} {[}Version 1.0.8; Mersmann, Trautmann, Steuer, and Bornkamp (2018){]}
\item
  Model fit and comparison: \emph{rstan} {[}Version 2.19.2; Stan Development Team (2019a){]}, \emph{brms} {[}Version 2.13.0; Bürkner (2017); Bürkner (2018){]}, \emph{BayesFactor} {[}Version 0.9.12.4.2; Morey and Rouder (2018){]}, \emph{bridgesampling} {[}Version 1.0.0; Gronau, Singmann, and Wagenmakers (2020){]}
\item
  Visualization: \emph{coda} {[}Version 0.19.3; Plummer, Best, Cowles, and Vines (2006){]}, \emph{lattice} {[}Version 0.20.38; Sarkar (2008){]}, \emph{ggplot2} {[}Version 3.3.2; Wickham (2016){]}, \emph{Rmisc} {[}Version 1.5; Hope (2013){]}, \emph{devtools} {[}Version 2.2.1; Wickham, Hester, and Chang (2019){]}, \emph{gghalves} {[}Version 0.1.0; Tiedemann (2020){]}, \emph{bayesplot} {[}Version 1.7.1; Gabry, Simpson, Vehtari, Betancourt, and Gelman (2019){]}, \emph{gridExtra} {[}Version 2.3; Auguie (2017){]}, \emph{tibble} {[}Version 3.0.2; Müller and Wickham (2019){]}, \emph{ggmcmc} {[}Version 1.4.1; Fernández-i-Marín (2016){]}, \emph{cowplot} {[}Version 1.0.0; Wilke (2019){]}, \emph{ggridges} {[}Version 0.5.1; Wilke (2018){]}, \emph{circlize} {[}Version 0.4.9; Gu, Gu, Eils, Schlesner, and Brors (2014){]}, \emph{StanHeaders} {[}Version 2.19.0; Stan Development Team (2019b){]}, \emph{unikn} {[}Version 0.2.0; Neth and Gradwohl (2019){]}, \emph{ggbeeswarm} {[}Version 0.6.0; Clarke and Sherrill-Mix (2017){]}
\item
  Other: \emph{Rcpp} {[}Version 1.0.3; Eddelbuettel and François (2011); Eddelbuettel and Balamuta (2017){]}, \emph{usethis} {[}Version 1.5.1; Wickham and Bryan (2019){]}
\end{itemize}

>>>>

\hypertarget{declarations}{%
\section{Declarations}\label{declarations}}

\hypertarget{funding}{%
\subsection{Funding}\label{funding}}

This work was supported in part by an NWO Research Talent grant to A.M.S. (406.18.556) and a Veni grant from the NWO (VI.Veni.201G.019) to J.M.H.

\hypertarget{conflicts-of-interest}{%
\subsection{Conflicts of interest}\label{conflicts-of-interest}}

The authors have no conflicts of interest to declare.

\hypertarget{availability-of-data-and-materials}{%
\subsection{Availability of data and materials}\label{availability-of-data-and-materials}}

We do not have ownership of the data used in this study, but the the data set is publicly available on \href{https://github.com/PerceptionCognitionLab/data0/blob/master/lexDec-dist5/}{GitHub}. The \texttt{.stan} models, results of the model fit, and model comparison are available on \href{}{our GitHub repository}.

\hypertarget{code-availability}{%
\subsection{Code availability}\label{code-availability}}

The R code used for the analyses and figures in this manuscript, and \texttt{R} tutorials on BHMs are available under an CC-BY-4.0 license on \href{}{our GitHub repository}.

\hypertarget{authors-contributions}{%
\subsection{Authors' contributions}\label{authors-contributions}}

M.V. participated in the design and coordination of this study, performed statistical analyses, and drafted the paper; A.S. participated in the design and coordination of this study, helped with the statistical analyses, interpretation of the results and writing the paper; J.H. (principal investigator) conceived the study, participated in the design and coordination of the study, helped with the statistical analyses, interpretation of results and writing the paper. All authors read and approved the final paper.

\hypertarget{acknowledgements}{%
\subsection{Acknowledgements}\label{acknowledgements}}

@@

\begin{itemize}
\tightlist
\item
  Document layout: \emph{rmarkdown} {[}Version 2.9; Xie, Allaire, and Grolemund (2018){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2018){]}, \emph{knitr} {[}Version 1.33; Xie (2015){]}, \emph{kableExtra} {[}Version 1.3.4; Zhu (2019){]}
\item
  Data analysis and cleaning: \emph{LaplacesDemon} {[}Version 16.1.6; Statisticat and LLC. (2020){]}, \emph{plyr} {[}Version 1.8.6; Wickham, François, Henry, and Müller (2019); Wickham (2011){]}, \emph{dplyr} {[}Version 1.0.7; Wickham, François, Henry, and Müller (2019){]}, \emph{readr} {[}Version 2.0.0; Wickham, Hester, and Francois (2018){]}, \emph{crch} {[}Version 1.0.4; Messner, Mayr, and Zeileis (2016); Messner, Mayr, and Zeileis (2017); Messner, Zeileis, Broecker, and Mayr (2014); Messner, Mayr, Zeileis, and Wilks (2014){]}, \emph{foreign} {[}Version 0.8.81; R Core Team (2018){]}, \emph{Matrix} {[}Version 1.3.3; Bates and Maechler (2019){]}, \emph{tidyr} {[}Version 1.1.3; Wickham and Henry (2019){]}, \emph{truncnorm} {[}Version 1.0.8; Mersmann, Trautmann, Steuer, and Bornkamp (2018){]}
\item
  Model fit and comparison: \emph{rstan} {[}Version 2.21.3; Stan Development Team (2019a){]}, \emph{brms} {[}Version 2.16.3; Bürkner (2017); Bürkner (2018){]}, \emph{BayesFactor} {[}Version 0.9.12.4.2; Morey and Rouder (2018){]}, \emph{bridgesampling} {[}Version 1.1.2; Gronau, Singmann, and Wagenmakers (2020){]}
\item
  Visualization: \emph{coda} {[}Version 0.19.4; Plummer, Best, Cowles, and Vines (2006){]}, \emph{lattice} {[}Version 0.20.44; Sarkar (2008){]}, \emph{ggplot2} {[}Version 3.3.5; Wickham (2016){]}, \emph{Rmisc} {[}Version 1.5; Hope (2013){]}, \emph{devtools} {[}Version 2.4.2; Wickham, Hester, and Chang (2019){]}, \emph{gghalves} {[}Version 0.1.1.9000; Tiedemann (2020){]}, \emph{bayesplot} {[}Version 1.8.1; Gabry, Simpson, Vehtari, Betancourt, and Gelman (2019){]}, \emph{gridExtra} {[}Version 2.3; Auguie (2017){]}, \emph{tibble} {[}Version 3.1.6; Müller and Wickham (2019){]}, \emph{ggmcmc} {[}Version 1.5.1.1; Fernández-i-Marín (2016){]}, \emph{cowplot} {[}Version 1.1.1; Wilke (2019){]}, \emph{ggridges} {[}Version 0.5.3; Wilke (2018){]}, \emph{circlize} {[}Version 0.4.13; Gu, Gu, Eils, Schlesner, and Brors (2014){]}, \emph{StanHeaders} {[}Version 2.21.0.7; Stan Development Team (2019b){]}, \emph{unikn} {[}Version 0.4.0; Neth and Gradwohl (2019){]}, \emph{ggbeeswarm} {[}Version 0.6.0; Clarke and Sherrill-Mix (2017){]}
\item
  Other: \emph{Rcpp} {[}Version 1.0.7; Eddelbuettel and François (2011); Eddelbuettel and Balamuta (2017){]}, \emph{usethis} {[}Version 2.0.1; Wickham and Bryan (2019){]}
\end{itemize}
